Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line

### 2024-03-21 manuscript_thev_transcriptome.tex
rerun entire workflow after rebuilding environment

\setlength{\tabcolsep}{0pt}

@@

\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\

@@

\endfoot

>>>>

\setlength{\tabcolsep}{2pt}

@@

\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\

@@

\endlastfoot
